Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-06-20 paper.tex
Iterate and move related work
Pass on NGE experiments and scattered space savings
PanDA Broker Architecture and anonymization
minor refinement of introduction.
  remove abstract to give to Jack et al.
Iteration 4 and scattered editing
Iteration conclusions
Clean up
Iteration introduction
space saving. 5 lines over.
down to 10!
Negative spaces fixing
fixing text over run / S7.
Fix spaces
Convert paper to IEEETran style for eScience conference

\documentclass[sigconf, screen]{acmart}

@@

% DOI
% \acmDOI{10.475/123_4}

% ISBN
% \acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[SC2017]{The International Conference for High Performance Computing, Networking, Storage and Analysis}{November 2017}{Denver, Colorado USA}
\acmYear{2017}
\copyrightyear{2017}

% \acmPrice{15.00}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

% -----------------------------------------------------------------------------
% BEGIN DOCUMENT
% -----------------------------------------------------------------------------
\begin{document}

\title{A Case Study on Abstractions to Converge High-Throughput and High-Performance Computing}

\author{Author 1}
\affiliation{\institution{Institution 1}}
\email{email1}

\author{Author 2}
\affiliation{\institution{Institution 2}}
\email{email2}

\author{Author 3}
\affiliation{\institution{Institution 3}}
\email{email3}

\author{Author 4}
\affiliation{\institution{Institution 4}}
\email{email4}

\author{Author 5}
\affiliation{\institution{Institution 5}}
\email{email5}

\author{Author 6}
\affiliation{\institution{Institution 6}}
\email{email6}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{Author 1 et al.}

% ----------------------------------------------------------------------------
% ABSTRACT
% ----------------------------------------------------------------------------
\begin{abstract}
\input{abstract}
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
\end{CCSXML}

% \ccsdesc[500]{Computer systems organization~Embedded systems}
% \ccsdesc[300]{Computer systems organization~Redundancy}
% \ccsdesc{Computer systems organization~Robotics}
% \ccsdesc[100]{Networks~Network reliability}

\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle

% ----------------------------------------------------------------------------
% I - INTRODUCTION
% ----------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}

\input{introduction}

% ----------------------------------------------------------------------------
% II - RELATED WORK
% ----------------------------------------------------------------------------
\section{Related Work}
\label{sec:related}

% \input{WMSLiterature}
% Please do not correct bckground to background.
\input{bckground}

% ----------------------------------------------------------------------------
% III - PanDA OVERVIEW
% ----------------------------------------------------------------------------
\section{PanDA Overview}
\label{sec:panda_overview}

\input{PandaOverview}

% ----------------------------------------------------------------------------
% IV - DEPLOYING PANDA ON A LEADERSHIP-SCALE SYSTEM
% ----------------------------------------------------------------------------
\section{Deploying PanDA on a Leadership-scale system}
\label{sec:panda_deployment}

\input{PandaEvolution}

% ----------------------------------------------------------------------------
% V - ANALYSIS AND DISCUSSION
% ----------------------------------------------------------------------------
\section{Analysis and Discussion}
\label{sec:panda_titan}

\input{overall}

% ----------------------------------------------------------------------------
% VII - THE NEXT GENERATION EXECUTOR
% ----------------------------------------------------------------------------
% \section{PANDA: Future/RoadMap}
\section{PANDA\@: The Next Generation Executor}
\label{sec:panda_roadmap}

\input{nge}
\input{Experiments}

% ----------------------------------------------------------------------------
% VIII - CONCLUSION
% ----------------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

\input{conclusion}

% ----------------------------------------------------------------------------
% ACKNOWLEDGEMENTS
% ----------------------------------------------------------------------------
\section*{Acknowledgements}
\label{sec:ack}

\input{ack}

% ----------------------------------------------------------------------------
% REFERENCES
% ----------------------------------------------------------------------------
\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

>>>>

\documentclass[conference]{IEEEtran}

% ---------------------------------------------------------------------------
% Authors are invited to submit unpublished, original work, using the IEEE
% 8.5 × 11 manuscript guidelines: double-column text using single-spaced 10
% point font on 8.5 × 11 inch pages. Templates are available from http://www.
% ieee.org/conferences_events/conferences/publishing/templates.html.
%
% The conference proceedings will be made available online through the IEEE
% Digital Library.
%
% Three types of papers will be accepted:
%
% - Full research papers (up to 10 pages): focus on new research achievements
%   in eScience, spanning core technologies and applications.
% - Experience papers (up to 10 pages): focus on practical outcomes through
%   applying eScience tools and techniques to novel problems.
% ---------------------------------------------------------------------------

@@

% ---------------------------------------------------------------------------
% BEGIN DOCUMENT
% ---------------------------------------------------------------------------
\begin{document}

\title{Converging High-Throughput and High-Performance Computing: A Case Study}

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
% \author{
%     \IEEEauthorblockN{
%         Author 1\IEEEauthorrefmark{1},
%         Author 2\IEEEauthorrefmark{2},
%         Author 3\IEEEauthorrefmark{3}, 
%         Author 4\IEEEauthorrefmark{3}, 
%         Author 5\IEEEauthorrefmark{4} and
%         Author 6\IEEEauthorrefmark{4}
%     }
%     \IEEEauthorblockA{
%         \IEEEauthorrefmark{1}Department\\Institution, address, email
%     }
%     \IEEEauthorblockA{
%         \IEEEauthorrefmark{2}Department\\Institution, address, email
%     }
%     \IEEEauthorblockA{
%         \IEEEauthorrefmark{3}Department\\Institution, address, email
%     }
%     \IEEEauthorblockA{
%         \IEEEauthorrefmark{4}Department\\Institution, address, email
%     }
% }

% ---------------------------------------------------------------------------
% ABSTRACT
% ---------------------------------------------------------------------------
\maketitle
\begin{abstract}
\input{abstract}
\end{abstract}
% \keywords{Distributed computing, Workload management system}

% ---------------------------------------------------------------------------
% I - INTRODUCTION
% ---------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}
\input{introduction}

% ---------------------------------------------------------------------------
% II - PanDA OVERVIEW
% ---------------------------------------------------------------------------
\section{PanDA Overview}
\label{sec:panda_overview}
\input{PandaOverview}

% ---------------------------------------------------------------------------
% III - DEPLOYING PANDA ON A LEADERSHIP-SCALE SYSTEM
% ---------------------------------------------------------------------------
%\section{Deploying PanDA on a Leadership-scale system}
\section{Deploying PanDA on Titan}
\label{sec:panda_titan}
\input{PandaEvolution}

% ---------------------------------------------------------------------------
% IV - ANALYSIS AND DISCUSSION
% ---------------------------------------------------------------------------
\section{Analysis and Discussion}
\label{sec:panda_titan}
\input{overall}

% ---------------------------------------------------------------------------
% VI - THE NEXT GENERATION EXECUTOR
% ---------------------------------------------------------------------------
% \section{PANDA: Future/RoadMap}
\section{PANDA\@: The Next Generation Executor}
\label{sec:panda_roadmap}
\input{nge}
\input{Experiments}

% ---------------------------------------------------------------------------
% VII - RELATED WORK
% ---------------------------------------------------------------------------
%\vspace{-0.4in}
\section{Related Work}
\label{sec:related}
\input{bckground}

% ---------------------------------------------------------------------------
% VIII - CONCLUSION
% ---------------------------------------------------------------------------
%\vspace{-0.1in}
\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}

% ---------------------------------------------------------------------------
% ACKNOWLEDGEMENTS
% ---------------------------------------------------------------------------
% \section*{Acknowledgements}
% \label{sec:ack}
%
% \input{ack}

% ---------------------------------------------------------------------------
% REFERENCES
% ---------------------------------------------------------------------------
\newpage
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,bibliography}

% ---------------------------------------------------------------------------
% A - APPENDIX
% ---------------------------------------------------------------------------
% \appendix
% \section{Artifact Description --- Converging High-Throughput and High-Performance Computing: A Case Study}
% \label{apnx:ac}
% \input{appendix}
